### 2020-01-24 overview.tex
Chapter 5.

The investigations presented in this thesis are motivated by the interest in understanding droplet interactions and suspension flow that originates from a number of applications, including material science, microfluidic technology and transport of complex fluids.
The general physical picture and underlying mathematical formulation are described in Chapter \ref{chp:micro-hydro}, where we introduce the elementary properties of the Stokes flow and its approximate solutions in the presence of liquid droplets or solid particles in a few simple cases.
These are the fundamentals of microhydrodynamics, essential for building a physical intuition and making back-of-the-envelope estimates when faced with more complicated engineering problems.
Unfortunately, sometimes a problem may be too complicated to be solved analytically, or we may simply be misguided by our intuitions.
In those cases, numerical simulations offer a relatively inexpensive means to visualise fluid motions and disentangle the various effects.
Therefore, Chapter \ref{chp:num-methods} provides a mini-review of some currently popular methods that can be applied to simulate coupled multiphase systems.
This is the main subject of the present work -- we develop methods, implement algorithms, and simulate droplets or particles in fluids to reproduce experiments or verify theories.
The specific aim may differ by applications; what remains the same is the numerical approach to problem solving as well as a curiosity-driven effort to uncover more physical principles.

\begin{figure}%[b]
  \centering
  \includegraphics[width=0.95\columnwidth]{paper-diagram.pdf}
  \caption{Diagrammatic representation of the papers in Part II parameterized by the number of droplets ($N$) that are or could potentially be studied, and by the distance (indicated by color) to being purely experimental ($-1$) or purely theoreticaly ($1$); 0 corresponds to purely numerical. Note that \emph{Paper 6} does not have a meaningful definition of $N$.}
  \label{fig:p-diagram}
\end{figure}

The detailed results of the present work are given in the next part of the thesis in the format of journal articles or technical reports.
Among them, 
Papers 1--4 entail droplet interactions,
Papers 5 \& 6 are miscellaneous, and
Paper 7 concerns suspension flow.
Separate summaries of each paper are given in the beginning of Part II.
A diagrammatic categorization is also illustrated in Figure \ref{fig:p-diagram}.
Overall, the common limitation of the conducted studies is the lack of a simple quantitative model that predicts the main phenomenon.
It is quite often the case that weak qualitative conclusions are drawn from the simulations, and a new set of simulations may have to be performed in very different conditions.

Finally, as a outlook to future studies, lessons learned from the present thesis include:
(i) Flow-assisted droplet assembly for photonic crystals is not straightforward. Perhaps disorder materials.
(ii) Level set methods are mass-leaking; not recommended for solving engineering problems for its own sake. But it is still fun to develop methods and it may have other applications, such as modelling tissue growth.
(iii) IB simulations for particle interactions are very slow. Patience.
(iv) Droplets in turbulence is an exciting new avenue, a lot to simulate and model.
(v) Wetting is important but nasty.
(vi) Dense suspension is very exciting, many parameters to do, very interesting from a theoretical point of view, also can be a testbed for new methods.

>>>>

The investigations presented in this thesis are motivated by the interest in understanding droplet interactions and suspension flow
that originates from a number of applications, including material science, microfluidic technology and transport of complex fluids.
The general physical picture and underlying mathematical formulation are described in Chapter \ref{chp:micro-hydro},
where we introduce elementary properties of the Stokes flow and its approximate solutions in the presence of liquid droplets or solid particles in a few simple cases.
These are the fundamentals of microhydrodynamics,
essential for developing a physical intuition and making back-of-the-envelope estimates when faced with more complicated engineering problems.
Unfortunately, sometimes a problem may be too complicated to be solved analytically, or we may simply be misguided by our intuitions.
In those cases, numerical simulations offer a relatively inexpensive means to visualise fluid motions and disentangle the various effects.
Therefore, Chapter \ref{chp:num-methods} provides a mini-review of some currently popular methods that can be applied to simulate coupled multiphase systems.
This is the main subject of the present work --
we develop methods, implement algorithms, and simulate droplets or particles in fluids to reproduce experiments or verify theories.
The specific aim may differ by applications;
what remain the same are the numerical approach to problem solving as well as a physics-oriented search for new principles driven by curiosity.

\begin{figure}%[b]
  \centering
  \includegraphics[width=0.95\columnwidth]{paper-diagram.pdf}
  \caption{Diagrammatic representation of the papers in Part II parameterized by the number of droplets ($N$) that are or could potentially be studied,
  and by the distance (indicated by color) to being purely experimental ($-1$) or purely theoreticaly ($1$); 0 corresponds to purely numerical.
  The papers are labelled with short titles. Note that \emph{Paper 6} does not have a meaningful definition of $N$.}
  \label{fig:p-diagram}
\end{figure}

The detailed results of the present work are given in the next part of the thesis in the format of journal articles or technical reports.
Among them, 
papers 1--4 entail droplet interactions,
papers 5 \& 6 are miscellaneous, and
paper 7 concerns suspension flow.
Separate retrospective summaries of each paper are given in the beginning of Part II.
A diagrammatic categorization is also illustrated in Figure \ref{fig:p-diagram}.
Overall, the common limitations of the conducted studies are that simulations still fall much behind experiments in terms of physical complexity
(which could be justified, but it is still not the same) and
the lack of simple quantitative models that can be extracted from the results.
In general, simulations provide additional evidences to conclude qualitatively,
but a new set of simulations or experiments may have to be performed in different situations.

Finally, as an outlook, we summarise the lessons learned during the course of this thesis and name a few open questions worth further research:
\medskip

\begin{itemize}
 \item Fabricating photonic crystals using flow-assisted droplet assembly could potentially achieve a moderate bang gap and be scaled up to meet industrial needs.
 The rest of the task is in engineering.
 Current focus of the photonic community seems to be shifted to searching for disordered hyperuniform materials
 that are easily to make and still possess bandgaps \citep{Torquato_review_2018, Joshua_2017PRL}.
 \medskip

 \item For multiphase flow simulations, classical level set methods are not mass conserving,
 thus many efforts (including the present work) have been spent to improve its accuracy.
 Despite all the progress, it remains a challenge to devise a general-purpose solver that can be applied to any multiphase flow problems without any tweaking,
 given the large separation of length scales and inherent singularities.
 In retrospect, the simulation of droplet assembly in microfluidic environments could be done with available open-source softwares instead of inventing a new method.
 However, the latter process is rewarding for its own sake,
 and the resulting method may be adapted to study plenty of other unforeseen applications, such as tissue growth modelling.

 %\item Droplets in turbulence is an exciting new avenue, a lot to simulate and model.
 \medskip

 \item Wetting is important in many practical applications; but assumptions made in many numerical work are often too crude to be trusted fully.
 Careful and rigorous simulations, along with accurate experiments, are needed to develop better models for processes involving interfaces moving on solid surfaces.
 \medskip

 \item Dense particle suspension is a very exciting research front,
 offers an immense parameter space to explore,
 and is related to both applied and fundamental questions.
 For example, questions like how particle geometry affects jamming,
 do active particles jam in the same way as passive particles,
 how do particle interactions and the medium topology come into play in long time limits (relavant to certain disease progression, \eg Alzheimer's disease), \etc
 are all unknown today.
 Investigating these problems requires development of new computational models and collaboration with specialists in different research areas,
 and may inspire new pathways to advance life science and biology in the future.
\end{itemize}
